### 2015-03-20 swmpr_manu.tex
started swmpr applications section, redo metab estimates for all data

\paragraph{Data retrieval}

\ac{SWMP} data must be obtained from the \ac{CDMO} prior to organizing and analyzing the information.  Two approaches can be used.  First, the data can be obtained outside of R using the online query forms on the \ac{CDMO} website (\href{http://cdmo.baruch.sc.edu/get/landing.cfm}{see here}).  Second, functions from the SWMPr package can be used to import the data directly from the online server (\Cref{tab:retrieve}).  In the latter case, the IP address for the computer making the request must be registered with \ac{CDMO}.  This can be done by following instructions \href{http://cdmo.baruch.sc.edu/webservices.cfm}{here}.  The \texttt{site\_codes} or \texttt{site\_codes\_ind} functions can be used to view the available metadata after a computer is registered with \ac{CDMO}.

% table for retrieval funcitons
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Data retrieval functions available from the SWMPr package.",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:retrieve",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Data retrieval functions available from the SWMPr package.\label{tab:retrieve}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{all\_params}&Retrieve up to 100 records starting with the most recent at a given station, all parameters.  Wrapper to \texttt{exportAllParamsXMLNew} function on web services.\tabularnewline
\texttt{all\_params\_dtrng}&Retrieve records of all parameters within a given date range for a station.  Optional argument for a single parameter.  Maximum of 1000 records. Wrapper to \texttt{exportAllParamsDateRangeXMLNew}.\tabularnewline
\texttt{import\_local}&Import files from a local path.  The files must be in a specific format, specifically those returned from the \ac{CDMO} using the zip downloads option for a reserve.\tabularnewline
\texttt{single\_param}&Retrieve up to 100 records for a single parameter starting with the most recent at a given station.  Wrapper to \texttt{exportSingleParamXMLNew} function on web services.\tabularnewline
\texttt{site\_codes}&Metadata for all stations, wrapper to \texttt{exportStationCodesXMLNew} function on web services.\tabularnewline
\texttt{site\_codes\_ind}&Metadata for all stations at a single site, wrapper  to \texttt{NERRFilterStationCodesXMLNew} function on web services.\tabularnewline
\hline
\end{tabular}\end{center}

@@

@@

@@

\hlcom{## plot}
\hlkwd{plot_summary}\hlstd{(dat,} \hlkwc{param} \hlstd{=} \hlstr{'chla_n'}\hlstd{)}
\end{alltt}
\end{kframe}\begin{figure}[!ht]

@@

Estimates of ecosystem metabolism provide a useful measure of overall system productivity.  These estimates are commonly used to evaluate whether an ecosystem is a net source or sink of organic material.  The open-water method is a common approach to quantify net ecosystem metabolism using a mass balance equation that describes the change in dissolved oxygen over time from the balance between photosynthetic and respiration rates, corrected for air-sea gas diffusion at the surface \cite{Odum56}.  The diffusion-corrected DO flux estimates are averaged during day and night for each 24 hour period in the time series, where flux is an hourly rate of DO change. DO flux is averaged during night hours for respiration and averaged during day hours for net production. Respiration rates are assumed constant during day and night such that total daily rates are calculated as hourly respiration multiplied by 24. The metabolic day is considered the 24 hour period between sunsets on two adjacent calendar days.  Respiration is subtracted from daily net production estimates to yield gross production.

The \texttt{ecometab} function is used to implement an adaptation of the open-water method \cite{Odum56,Caffrey14}.  Several assumptions must be met for a valid interpretation of the results.  In general, the dissolved oxygen time series is assumed to represent the same water mass over time.  Tidal advection may have a significant influence on the time series, which can contribute to a significant amount of noise in metabolic estimates.  The extent to which tidal advection influences the dissolved oxygen signal depends on various site-level characteristics and an intimate knowledge of the site may be required.  Volumetric rates for gross production and total respiration are also based on total depth of the water column, which is assumed to be mixed.  Water column depth is based on mean value for the depth variable across the time series and is floored at 1 meter for very shallow stations.  Additionally, the volumetric reaeration coefficient requires an estimate of the anemometer height of the weather station, which is set as 10 meters by default.  The metadata should be consulted for exact height. Other assumptions may apply and the user should consult the relevant literature (see the references in the help file).  All estimates are in mmol of oxygen but can be converted  to grams by changing the default arguments (i.e., 1mmol O2 = 32 mg O2, 1000 mg = 1g, multiply all estimates by 32/1000).

The following is an example that shows how to use the function from a combined water quality and weather data set.  The results can be plotted using \texttt{plot\_metab} (\Cref{metab_ex}).

@@

\paragraph{Miscellaneous functions}

Several additional functions are provided that cannot be described by the above categories.  These functions are generally used within the main functions but may be useful for more customized evaluation of \ac{SWMP} data.

Finally, a reserve map with all stations can be obtained using the \texttt{map\_reserve} function.  This function is a simple wrapper to functions in the ggmap package \cite{ggmap13}. The current function is limited to Google maps, which allows four map types that can be set with the \texttt{map\_type} argument: terrain (default), satellite, roadmap, or hybrid.  The \texttt{zoom} argument may have to be chosen through trial and error depending on the spatial extent of the reserve.  See the help documentation for ggmap for more info on zoom.

@@

\subsection*{Function list}

\paragraph{Organize}

\texttt{comb.swmpr} Combines \texttt{swmpr} objects to a common time series using setstep, such as combining the weather, nutrients, and water quality data for a single station. Only different data types can be combined.

\texttt{qaqc.swmpr} Remove QAQC columns and remove data based on QAQC flag values for a \texttt{swmpr} object.  Only applies if QAQC columns are present.

\texttt{qaqcchk.swmpr} View a summary of the number of observations in a \texttt{swmpr} object that are assigned to different QAQC flags used by \ac{CDMO}.  The output is used to inform further processing but is not used explicitly.

\texttt{rem\_reps.swmpr} Remove replicate nutrient data that occur on the same day.  The default is to average replicates.

\texttt{setstep.swmpr} Format data from a \texttt{swmpr} object to a continuous time series at a given timestep.  The function is used in \texttt{comb.swmpr} and can also be used with individual stations.

\texttt{subset.swmpr} Subset by dates and/or columns for a \texttt{swmpr} object.  This is a method passed to the generic \texttt{subset} function provided in the base package.

\paragraph{Analyze}

\texttt{aggregate.swmpr} Aggregate \texttt{swmpr} objects for different time periods - years, quarters, months,  weeks, days, or hours.  Aggregation function is user-supplied but defaults to mean.

\texttt{aggregate\_metab} Aggregate metabolism data from a \texttt{swmpr} object.  This is primarly used within \texttt{plot\_metab} but may be useful for simple summaries of raw daily data.

\texttt{ecometab.swmpr} Estimate ecosystem metabolism for a combined water quality and weatehr dataset using the open-water method.

\texttt{decomp.swmpr} Decompose a \texttt{swmpr} time series into trend, seasonal, and residual components.  This is a simple wrapper to \texttt{decompose}.  Decomposition of monthly or daily trends is possible.

\texttt{decomp\_cj.swmpr} Decompose a \texttt{swmpr} time series into grandmean, annual, seasonal, and events components.  This is a simple wrapper to \texttt{decompTs} in the wq package.  Only monthly decomposition is possible.

\texttt{hist.swmpr} Plot a histogram for a \texttt{swmpr} object.

\texttt{lines.swmpr} Add lines to an existing \texttt{swmpr} plot.

\texttt{na.approx.swmpr} Linearly interpolate missing data (\texttt{NA} values) in a \texttt{swmpr} object. The maximum gap size that is interpolated is defined as a maximum number of records with missing data.

\texttt{plot.swmpr} Plot a univariate  time series for a \texttt{swmpr} object.  The parameter name must be specified.

\texttt{plot\_metab} Plot ecosystem metabolism estimates after running \texttt{ecometab} on a \texttt{swmpr} object.

\texttt{plot\_summary} Create summary plots of seasonal/annual trends and anomalies for a water quality or weather parameter.

\texttt{smoother.swmpr} Smooth \texttt{swmpr} objects with a moving window average.  Window size and sides can be specified, passed to \texttt{filter}.

\paragraph{Miscellaneous}

\texttt{calcKL} Estimate the reaeration coefficient for air-sea gas exchange.  This is only used within the \texttt{ecometab} function.

\texttt{map\_reserve} Create a map of all stations in a reserve using the ggmap package.

\texttt{metab\_day} Identify the metabolic day for each approximate 24 period in an hourly time series.  This is only used within the \texttt{ecometab} function.

\texttt{param\_names} Returns column names as a list for the parameter type(s) (nutrients, weather, or water quality).  Includes QAQC columns with \texttt{f\_} prefix. Used internally in other functions.

\texttt{parser} Parses html returned from \ac{CDMO} web services, used internally in retrieval functions.

\texttt{swmpr} Creates object of \texttt{swmpr} class, used internally in retrieval functions.

\texttt{time\_vec} Converts time vectors to POSIX objects with correct time zone for a site/station, used internally in retrieval functions.

% Results and Discussion can be combined.
\section*{Results}

\section*{Discussion}

>>>>

\subsection*{Data retrieval}

\ac{SWMP} data must be obtained from the \ac{CDMO} prior to organizing and analyzing the information.  Two approaches can be used.  First, the data can be obtained outside of R using the graphical query forms on the \ac{CDMO} website (\href{http://cdmo.baruch.sc.edu/get/landing.cfm}{see here}).  Second, functions from the SWMPr package can be used to import the data directly from the online server using \ac{CDMO} web services (\Cref{tab:retrieve}).  In the latter case, the IP address for the computer making the request must be registered with \ac{CDMO}.  This can be done by following instructions \href{http://cdmo.baruch.sc.edu/webservices.cfm}{here}.  The \texttt{site\_codes} or \texttt{site\_codes\_ind} functions can be used to view the available metadata after a computer is registered with \ac{CDMO}.

% table for retrieval functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Retrieval functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?all\\_params} at the command line).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:retrieve",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Retrieval functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \texttt{?all\_params} at the command line).\label{tab:retrieve}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{all\_params}&Retrieve up to 100 records starting with the most recent at a given station, all parameters.  Wrapper to \texttt{exportAllParamsXMLNew} function on web services.\tabularnewline
\texttt{all\_params\_dtrng}&Retrieve records of all parameters within a given date range for a station.  Optional argument for a single parameter.  Maximum of 1000 records. Wrapper to \texttt{exportAllParamsDateRangeXMLNew}.\tabularnewline
\texttt{import\_local}&Import files from a local path.  The files must be in a specific format, specifically those returned from the \ac{CDMO} using the zip downloads option for a reserve.\tabularnewline
\texttt{single\_param}&Retrieve up to 100 records for a single parameter starting with the most recent at a given station.  Wrapper to \texttt{exportSingleParamXMLNew} function on web services.\tabularnewline
\texttt{site\_codes}&Metadata for all stations, wrapper to \texttt{exportStationCodesXMLNew} function on web services.\tabularnewline
\texttt{site\_codes\_ind}&Metadata for all stations at a single site, wrapper  to \texttt{NERRFilterStationCodesXMLNew} function on web services.\tabularnewline
\hline
\end{tabular}\end{center}

@@

% table for organize functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Organizing functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?comb.swmpr} at the command line).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:organize",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Organizing functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \texttt{?comb.swmpr} at the command line).\label{tab:organize}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{comb.swmpr}&Combines \texttt{swmpr} objects to a common time series using setstep, such as combining the weather, nutrients, and water quality data for a single station. Only different data types can be combined.\tabularnewline
\texttt{qaqc.swmpr}&Remove \ac{QAQC} columns and remove data based on \ac{QAQC} flag values for a \texttt{swmpr} object.  Only applies if \ac{QAQC} columns are present. \tabularnewline
\texttt{qaqcchk.swmpr}&View a summary of the number of observations in a \texttt{swmpr} object that are assigned to different \ac{QAQC} flags used by \ac{CDMO}.  The output is used to inform further processing but is not used explicitly.\tabularnewline
\texttt{rem\_reps.swmpr}&Remove replicate nutrient data that occur on the same day.  The default is to average replicates.\tabularnewline
\texttt{setstep.swmpr}&Format data from a \texttt{swmpr} object to a continuous time series at a given timestep.  The function is used in \texttt{comb.swmpr} and can also be used with individual stations.\tabularnewline
\texttt{subset.swmpr}&Subset by dates and/or columns for a \texttt{swmpr} object.  This is a method passed to the generic \texttt{subset} function provided in the base package.\tabularnewline
\hline
\end{tabular}\end{center}

@@

% table for analysis functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Analysis functions available from the SWMPr package.  Full documentation for each function is in the help file (e.g., execute \\texttt{?aggregate.swmpr} at the command line).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:analyze",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Analysis functions available from the SWMPr package.  Full documentation for each function is in the help file (e.g., execute \texttt{?aggregate.swmpr} at the command line).\label{tab:analyze}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{aggregate.swmpr}&Aggregate \texttt{swmpr} objects for different time periods - years, quarters, months,  weeks, days, or hours.  Aggregation function is user-supplied but defaults to mean.\tabularnewline
\texttt{aggregate\_metab.swmpr}&Aggregate metabolism data from a \texttt{swmpr} object.  This is primarly used within \texttt{plot\_metab} but may be useful for simple summaries of raw daily data.\tabularnewline
\texttt{ecometab.swmpr}&Estimate ecosystem metabolism for a combined water quality and weatehr dataset using the open-water method.\tabularnewline
\texttt{decomp.swmpr}&Decompose a \texttt{swmpr} time series into trend, seasonal, and residual components.  This is a simple wrapper to \texttt{decompose}.  Decomposition of monthly or daily trends is possible.\tabularnewline
\texttt{decomp\_cj.swmpr}&Decompose a \texttt{swmpr} time series into grandmean, annual, seasonal, and events components.  This is a simple wrapper to \texttt{decompTs} in the wq package.  Only monthly decomposition is possible.\tabularnewline
\texttt{hist.swmpr}&Plot a histogram for a \texttt{swmpr} object.\tabularnewline
\texttt{lines.swmpr}&Add lines to an existing \texttt{swmpr} plot.\tabularnewline
\texttt{na.approx.swmpr}&Linearly interpolate missing data (\texttt{NA} values) in a \texttt{swmpr} object. The maximum gap size that is interpolated is defined as a maximum number of records with missing data.\tabularnewline
\texttt{plot.swmpr}&Plot a univariate  time series for a \texttt{swmpr} object.  The parameter name must be specified.\tabularnewline
\texttt{plot\_metab.swmpr}&Plot ecosystem metabolism estimates after running \texttt{ecometab} on a \texttt{swmpr} object.\tabularnewline
\texttt{plot\_summary.swmpr}&Create summary plots of seasonal/annual trends and anomalies for a water quality or weather parameter.\tabularnewline
\texttt{smoother.swmpr}&Smooth \texttt{swmpr} objects with a moving window average.  Window size and sides can be specified, passed to \texttt{filter}.\tabularnewline
\hline
\end{tabular}\end{center}

@@

\hlcom{## plot}
\hlkwd{plot_summary}\hlstd{(dat,} \hlkwc{param} \hlstd{=} \hlstr{'chla_n'}\hlstd{,} \hlkwc{years} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{2007}\hlstd{,} \hlnum{2013}\hlstd{))}
\end{alltt}
\end{kframe}\begin{figure}[!ht]

@@

Estimates of ecosystem metabolism provide a useful measure of overall system productivity.  These estimates are commonly used to evaluate whether an ecosystem is a net source or sink of organic material.  The open-water method \cite{Odum56} is a common approach to quantify net ecosystem metabolism using a mass balance equation that describes the change in dissolved oxygen over time from the balance between photosynthetic and respiration processes, corrected using an empirically constrained air-sea gas diffusion model (see Ro and Hunt \cite{Ro06}, Thebault et al. \cite{Thebault08}). The diffusion-corrected \ac{DO} flux estimates are averaged separately over each day and night of the time series. The nighttime average \ac{DO} flux is used to estimate respiration rates, while the daytime \ac{DO} flux is used to estimate net primary production. To generate daily integrated rates, respiration rates are assumed constant such that hourly night time \ac{DO} flux rates are multiplied by 24. Similarly, the daytime \ac{DO} flux rates are multiplied by the number of daylight hours, which varies with location and time of year, to yield net daytime primary production. Respiration rates are subtracted from daily net production estimates to yield gross production rates. The metabolic day is considered the 24 hour period between sunsets on two adjacent calendar days

The \texttt{ecometab} function is used to implement an adaptation of the open-water method \cite{Odum56,Caffrey14}.  Several assumptions must be met for a valid interpretation of the results.  In general, the dissolved oxygen time series is assumed to represent the same water mass over time.  Tidal advection may have a significant influence on the time series, which can contribute to a significant amount of noise in metabolic estimates.  The extent to which tidal advection influences the dissolved oxygen signal depends on various site-level characteristics and an intimate knowledge of the site may be required.  Areal rates for gross production and total respiration are based on volumetric rates normalized to the depth of the water column at the sampling location, which is assumed to be well-mixed, such that the water quality sensor is reflecting the integrated processes in the entire water column (including the benthos).  Water column depth is calculated as the mean value of the depth variable across the time series in the \texttt{swmpr} object. Depth values are floored at one meter for very shallow stations and 0.5 meters is also added to reflect the practice of placing sensors slightly off of the bottom.  Additionally, the air-sea gas exchange model is calibrated with wind data either collected at, or adjusted to, wind speed at 10 m above the surface.  The metadata should be consulted for exact height. Other assumptions may apply and the user should consult the relevant literature.  All calculations within the function are done using molar units (e.g., mmol O$^2$ m$^{-3}$). The output can be returned as mass units by changing the default argument. Input data must be in standard mass units for \ac{DO} (mg L-1)

The following is an example that shows use of the function from a combined water quality and weather data set.  The results can be plotted using \texttt{plot\_metab} (\Cref{fig:metab_ex}).

@@

\subsection*{Miscellaneous functions}

Several additional functions are provided that do not fit the above categories (\Cref{tab:misc}).  These functions are generally used within the main functions but may be useful for more customized evaluation of \ac{SWMP} data.

% table for misc functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Miscellaneous functions available from the SWMPr package.  Most are used within the main functions above but may be useful for more customized evaluationg of \\ac{SWMP} data.  Full documentation for each function is in the help file (e.g., execute \\texttt{?calckl} at the command line).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:misc",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Miscellaneous functions available from the SWMPr package.  Most are used within the main functions above but may be useful for more customized evaluationg of \ac{SWMP} data.  Full documentation for each function is in the help file (e.g., execute \texttt{?calckl} at the command line).\label{tab:misc}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{calckl}&Estimate the reaeration coefficient for air-sea gas exchange.  This is only used within the \texttt{ecometab} function.\tabularnewline
\texttt{map\_reserve}&Create a map of all stations in a reserve using the ggmap package.\tabularnewline
\texttt{metab\_day}&Identify the metabolic day for each approximate 24 period in an hourly time series.  This is only used within the \texttt{ecometab} function.\tabularnewline
\texttt{param\_names}&Returns column names as a list for the parameter type(s) (nutrients, weather, or water quality).  Includes \ac{QAQC} columns with \texttt{f\_} prefix. Used internally in other functions.\tabularnewline
\texttt{parser}&Parses html returned from \ac{CDMO} web services, used internally in retrieval functions.\tabularnewline
\texttt{swmpr}&Creates object of \texttt{swmpr} class, used internally in retrieval functions.\tabularnewline
\texttt{time\_vec}&Converts time vectors to \texttt{POSIXct} objects with correct time zone for a site/station, used internally in retrieval functions.\tabularnewline
\hline
\end{tabular}\end{center}

For brevity, only the \texttt{reserve\_map} function is discussed.  This function can be used to create a map with all stations at a reserve by passing arguments to functions in the ggmap package \cite{ggmap13}. The current function is limited to Google maps of four types that can be set with the \texttt{map\_type} argument: terrain (default), satellite, roadmap, or hybrid.  The \texttt{zoom} argument may have to be chosen through trial and error depending on the spatial extent of the reserve.  See the help documentation for the \texttt{ggmap} function for more info on \texttt{zoom}.

@@

\section*{Applications using the SWMPr package}

The ability to evaluate environmental characteristics between estuaries within the \ac{NERRS} program has been greatly improved using functions in the SWMPr package.  This section describes two examples of applications using the SWMPr package to illustrate the improved ability to synthesize and evaluate multi-year time series of estuarine data.  First, the open-water method for estimating metabolism was applied to nearly all co-located water quality and weather sites at the \ac{NERRS} reserve for all years of available data.  The results are provided primarily to illustrate ease of use of the functions and secondarily to provide an update to results described in Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04}.  A comprehensive evaluation of metabolic rates between estuaries has not been conducted using the most recent \ac{SWMP} data.  The results are presented to facilitate additional research to evaluate factors that influence variation between sites.

Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04} describe the theory and application of the open-water method to estimate ecosystem metabolism using two sites at each of the \ac{NERRS} reserve.  Time series data included approximately five years of half-hour water quality observations at each site.  Additionally, the air-sea gas exchange model, as implemented by the current \texttt{ecometab} function (see Ro and Hunt \cite{Ro06} and Thebault et al. \cite{Thebault08}), was not incorporated into the initial metabolism estimates such that a constant value for the reaeration coefficient was assumed.  This coefficient provides an estimate of the rate of air-sea gas exchange that varies as a function of wind speed, temperature, barometric pressure, salinity, and depth of the water column  The inclusion of weather data in the calculation allows for a more precise estimate of air-sea gas exchange and consequently more reliable estimates of ecosystem metabolism (see Caffrey et al. \cite{Caffrey14} for details).

All water quality and weather observations for all \ac{NERRS} sites were obtained through a bulk data request in November of 2014 using the \href{http://cdmo.baruch.sc.edu/aqs/zips.cfm}{zip downloads} feature of \ac{CDMO}.  After the download was complete, all csv files for each station were imported into R using the \texttt{import\_local} function and then saved again on a local hard drive as a binary .RData file.  This resulted in a single \texttt{swmpr} object for each site.  All files were then uploaded to a remote server.  An R script was executed that retrieved and processed the \texttt{swmpr} objects for each site using the following functions in sequence:

\section*{Summary}
